\textsf{Are frontier models superhuman chemists?}

### 2024-03-11 src/tex/ms.tex
Update src/tex/ms.tex
Co-authored-by: Kevin M Jablonka <32935233+kjappelbaum@users.noreply.github.com>

\subparagraph{General chemistry}
The questions originate from examinations for grade X at Marist Comprehensive Academy Uturu, Nigeria. They cover fundamental concepts in chemistry suitable for students at the secondary school level.

\subparagraph{International Chemical Olympiad (\gls{ICHO})}
The questions are sourced from various countries' Chemical Olympiads, including those held in the USA, UK, and Moldova, providing challenging problems for competitive chemistry.

>>>>

\subparagraph{General chemistry}
The questions originate from 10th grade examinations at Marist Comprehensive Academy Uturu, Nigeria. They cover fundamental concepts in chemistry suitable for students at the secondary school level.

\subparagraph{International Chemical Olympiad (\gls{ICHO})}
The questions are sourced from various countries' Chemical Olympiads, including those held in the USA, UK, and Moldova.
